Hierarchically modelling \emph{Kepler} dwarfs and subgiants to improve inference of stellar properties with asteroseismology

### 2020-11-11 paper/main.tex
Ammended notation for ANN

An ANN is a network of artificial \emph{neurons} which each transform some input vector, $\boldsymbol{x}$ based on trainable weights, $\boldsymbol{w}$ and a bias, $b$. The weights are represented by the connections between neurons and the bias is a unique scalar associated with each neuron. A multi-layered ANN is where neurons are arranged into a series of layers such that any neuron in layer $k-1$ is connected to at least one of the neurons in layer $k$.

In this work, we considered a fully-connected ANN, where each neuron in layer $k-1$ is connected to every neuron in layer $k$. The output of the $i$-th neuron in layer $k$ is, 
%
\begin{equation}
    x_{i, k}=f_k(\boldsymbol{w}_{i, k} \cdot \boldsymbol{x}_{k-1} + b_{i, k})
\end{equation}
%
where $f_k$ is the \emph{activation} function for the $k$-th layer, $\boldsymbol{w}_{i, k}$ are the weights connecting all the neurons in layer $k-1$ to the current neuron, and $b_{i, k}$ is the bias. This generalises such that the output of the $k$-th layer is,
%
\begin{equation}
    \boldsymbol{x}_{k}=f_k(\boldsymbol{W}_{k} \cdot \boldsymbol{x}_{k-1} + \boldsymbol{b}_{k}),
\end{equation}
%
where $\boldsymbol{W}_k$ is the matrix of weights leading to all neurons in the $k$-th layer. For a regression ANN, we typically have a linear activation function applied to the output of the final layer. Therefore, the output of a network of $H$ hidden layers with initial input $\boldsymbol{\mathbb{X}}$ is,
%
\begin{equation}
    \widetilde{\boldsymbol{\mathbb{Y}}} = \boldsymbol{W}_{H} \cdot f_{H-1}(\dots f_1(\boldsymbol{W}_1 \cdot f_0(\boldsymbol{W}_{0} \cdot \boldsymbol{\mathbb{X}} + \boldsymbol{b}_{0}) + \boldsymbol{b}_1) ) + \boldsymbol{b}_{H}
\end{equation}
%
We also restricted our configuration to an ANN with the same number of neurons, $N$ in each hidden layer. Hereafter, we refer to our choice of neurons per layer, $N$ and hidden layers, $H$ as the \emph{architecture}.

To fit the ANN, we used a set of training data, $\boldsymbol{\mathbb{D}}_\mathrm{train} = \{(\boldsymbol{\mathbb{X}}_1, \boldsymbol{\mathbb{Y}}_1) \dots (\boldsymbol{\mathbb{X}}_{N_\mathrm{train}}, \boldsymbol{\mathbb{Y}}_{N_\mathrm{train}})\}$ comprising $N_\mathrm{train}$ input-output pairs. We split the training data into pseudo-random batches, $\boldsymbol{\mathbb{D}}_\mathrm{batch}$ because this has been shown to improve ANN stability and computational efficiency \citep{Masters.Luschi2018}. The set of predictions made for each batch is evaluated using a \emph{loss} function which primarily comprises an error function, $E(\boldsymbol{\mathbb{D}}_\mathrm{batch})$ to quantify the difference between the training outputs ($\boldsymbol{\mathbb{Y}}$) and predictions ($\widetilde{\boldsymbol{\mathbb{Y}}}$). We also considered an additional term to the loss called \emph{regularisation} which helps reduce over-fitting \citep{Goodfellow.Bengio.ea2016}. During fitting, the weights are updated after each batch using an algorithm called the \emph{optimizer}, back-propagating the error with the goal of minimising the loss \citep[see e.g.][]{Rumelhart.Hinton.ea1986} such that $\widetilde{\boldsymbol{\mathbb{Y}}} \approx \boldsymbol{\mathbb{Y}}$.

>>>>

An ANN is a network of artificial \emph{neurons} which each transform some input vector, $\boldsymbol{x}$ based on trainable weights, $\boldsymbol{w}$ and a bias, $b$. The weights are represented by the connections between neurons and the bias is a unique scalar associated with each neuron. A multi-layered ANN is where neurons are arranged into a series of layers such that any neuron in layer $j-1$ is connected to at least one of the neurons in layer $j$.

In this work, we considered a fully-connected ANN, where each neuron in layer $j-1$ is connected to every neuron in layer $j$. The output of the $k$-th neuron in layer $j$ is, 
%
\begin{equation}
    x_{j, k}=f_j(\boldsymbol{w}_{j, k} \cdot \boldsymbol{x}_{j-1} + b_{j, k})
\end{equation}
%
where $f_j$ is the \emph{activation} function for the $j$-th layer, $\boldsymbol{w}_{j, k}$ are the weights connecting all the neurons in layer $j-1$ to the current neuron, and $b_{j, k}$ is the bias. This generalises such that the output of the $j$-th layer is,
%
\begin{equation}
    \boldsymbol{x}_{j}=f_j(\boldsymbol{W}_{j} \cdot \boldsymbol{x}_{j-1} + \boldsymbol{b}_{j}),
\end{equation}
%
where $\boldsymbol{W}_j$ is the matrix of weights leading to all neurons in the $j$-th layer. For a regression ANN, we typically have a linear activation function applied to the output of the final layer. Therefore, the output of a network of $H$ hidden layers with initial input $\boldsymbol{\mathbb{X}}$ is,
%
\begin{equation}
    \widetilde{\boldsymbol{\mathbb{Y}}} = \boldsymbol{W}_{H} \cdot f_{H-1}(\dots f_1(\boldsymbol{W}_1 \cdot f_0(\boldsymbol{W}_{0} \cdot \boldsymbol{\mathbb{X}} + \boldsymbol{b}_{0}) + \boldsymbol{b}_1) ) + \boldsymbol{b}_{H}
\end{equation}
%
We also restricted our configuration to an ANN with the same number of neurons, $N$ in each hidden layer. Hereafter, we refer to our choice of neurons per layer, $N$ and hidden layers, $H$ as the \emph{architecture}.

To fit the ANN, we used a set of training data, $\boldsymbol{\mathbb{D}}_\mathrm{train} = \{\boldsymbol{\mathbb{X}}_i, \boldsymbol{\mathbb{Y}}_i\}_{i=1}^{N_\mathrm{train}}$ comprising $N_\mathrm{train}$ input-output pairs. We split the training data into pseudo-random batches, $\boldsymbol{\mathbb{D}}_\mathrm{batch}$ because this has been shown to improve ANN stability and computational efficiency \citep{Masters.Luschi2018}. The set of predictions made for each batch is evaluated using a \emph{loss} function which primarily comprises an error function, $E(\boldsymbol{\mathbb{D}}_\mathrm{batch})$ to quantify the difference between the training outputs ($\boldsymbol{\mathbb{Y}}$) and predictions ($\widetilde{\boldsymbol{\mathbb{Y}}}$). We also considered an additional term to the loss called \emph{regularisation} which helps reduce over-fitting \citep{Goodfellow.Bengio.ea2016}. During fitting, the weights are updated after each batch using an algorithm called the \emph{optimizer}, back-propagating the error with the goal of minimising the loss such that $\widetilde{\boldsymbol{\mathbb{Y}}} \approx \boldsymbol{\mathbb{Y}}$ \citep[see e.g.][]{Rumelhart.Hinton.ea1986}.
